Assessment and Optimization of Nowcast Measures for Trend Detection

### 2024-01-13 paper.tex
Update on Overleaf.

%%% --- Tabulars
\usepackage{booktabs}
\usepackage{multirow} % cells over several rows
\usepackage{tabularx}

@@

\begin{tabularx}{\textwidth}{c l l l}
     & Indicator & Weighted 1 & Weighted 2 \\
     Verrauschte Daten & & & \\
     Konzentration in Q1/Q3, aber viel an Entscheidungsgrenzen, kein Noise & & & \\
     $\ydiff_t = \xdiff_t$ und $\ydiff_t \sim N(0, 1)$ & & & \\

\end{tabularx}

>>>>

%%% --- Tabulars
\usepackage{booktabs}
\usepackage{multirow} % cells over several rows
\usepackage{tabularx}
\usepackage{tabularray}

@@

Compare the resulting trending assessments for the indicator formula and the weighted schemes. The horizontal axis displays $\ydiff$; the vertical axis corresponds to $\xdiff$. 
The plots show 200 points, but the estimations are computed on 10,000 points.

\noindent
\begin{tblr}{
  colspec = {Q[h]X[-1,m]X[-1,m]X[-1,m]|X[m]},
  width=\textwidth,
  stretch = 0,
  rowsep = 6pt,
}
     & Indicator & Weighted 1 & Weighted 2 & Remarks \\
     \includegraphics{plots/simulation_comparison_weighted_measures/simple.pdf} & 0.7705 & 0.7906 & &  \\
     \includegraphics{plots/simulation_comparison_weighted_measures/concordant_no_noise.pdf} & 1 & 1 &  & {\scriptsize$\xdiff = \xdifft = 0.05 \ydifft = 0.05 \ydiff$}\newline critique on w1: slight deviation of $\xdiff$ from 0 (near decision boundary), nevertheless, full trending ability. \\
     \includegraphics{plots/simulation_comparison_weighted_measures/concordant_noise.pdf} & 0.6485 & 0.6835 & \\
     \includegraphics{plots/simulation_comparison_weighted_measures/perfect_normal.pdf} & 1 & 1 & & critique on w2: $\xdiff = \ydiff$, but not trending ability 1\\

     \includegraphics{plots/simulation_comparison_weighted_measures/sure_unsure_combination.pdf} & 0.6152 & 0.6932 & & \\
\end{tblr}
